\documentclass[11pt, titlepage]{article}  % , titlepage
\usepackage{Sections/Common/toshi}
%\usepackage{comment}


\begin{document}


\definecolor{labelkey}{rgb}{1,1,1}    % hide label keys
\renewcommand{\include}[1]{}
%\renewcommand\documentclass[2][]{}


\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\setcounter{page}{0}
%%%%%%%%%%%%%%%%% Title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}


% paper/preprint number
\begin{flushright}
Dissertation
%RIKEN-iTHEMS-Report-?? \\
%OU-HET-???
\end{flushright}



% title
\vskip5cm%\vskip3cm
\begin{center}
{\LARGE {\bf Defects in Supersymmetric Gauge Theory  \\
\vspace{0.4cm}
and Integrable Lattice Models}}



% name
\vskip3cm%\vskip1.5cm
{\large
\bf {Toshihiro Ota} %$^{a, b}$\footnote{\href{mailto:toshihiro.ota@riken.jp}{toshihiro.ota@riken.jp}}
}



% affiliation
\vskip3cm%\vskip1cm
%\it ${}^{a}$RIKEN Interdisciplinary Theoretical \& Mathematical Sciences Program (iTHEMS), \\
%Wako, Saitama 351-0198, Japan \\
%\it ${}^{b}$
\it Department of Physics, Osaka University,  Toyonaka, Osaka 560-0043, Japan
\end{center}



%\newpage
%\vskip1cm
\begin{abstract} %abstract
\centering
\begin{minipage}{12.32cm}  % 12.32=0.8*15.4,  15.4cm=\textwidth
In this thesis, we investigate correspondences between
supersymmetric gauge theories and integrable lattice models,
in the presence of additional defect operators.
We describe a general prescription to construct the correspondence
using branes in string theory, which allows us to study
integrable structures in a large class of quiver gauge theories
in a systematic way.
We compute supersymmetric indices in the presence of defect operators,
and verify that they are identified with transfer matrices of
integrable lattice models.
The relation between the brane realization of the correspondence and
the theories of class-$\CS$ is also considered.
We clarify how our framework can be related to four-dimensional analogue
of Chern-Simons theory through brane setups in string theory and dualities.
\end{minipage}
\end{abstract}



\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I would like to thank \dots.
\begin{comment}
I would like to acknowledge kind support and help from many people,
without those this thesis would not have been completed.
Firstly, I would like to thank my Ph.D.~advisor Koji Hashimoto
who has given me great opportunity to start my study of string theory at Osaka university.
In particular, in the first three years of my Ph.D.~program I could learn
a lot of things through discussion and collaboration with him.
I owe deep gratitude to my collaborators Kazunobu Maruyoshi and Junya Yagi.
This thesis is largely based on the joint work with them,
and I have been enjoying discussion and chat with them every time.
They brought me to the fascinating subject at the intersection of supersymmetric gauge theory,
string theory, and integrable system.
I am also grateful to Yasuhiro Akutsu, Norihiro Iizuka, Tetsuya Onogi and Satoshi Yamaguchi
for reading the manuscript of this thesis carefully and giving me useful comments.

I would like to say how much of a pleasure it has been being a member of iTHEMS at RIKEN.
In particular, I profoundly thank Tetsuo Hatsuda, who is the director of iTHEMS, and Masato Taki,
who was a member of iTHEMS and is also my collaborator on machine learning.
I really appreciate their advice, encouragement, and arrangement during my life at iTHEMS.
Over the past two years, I have been greatly benefited from stimulating discussions with
colleagues in various fields of science at iTHEMS.
Such an experience has made my Ph.D.~course quite fruitful and way more enjoyable.
I am especially indebted to mathematicians at iTHEMS; Hokuto Konno, Genki Ouchi,
Kenta Sato and Masaki Taniguchi for communicating with and telling me lots of mathematical ideas.
Inspiring discussions and interesting conversation with them were a great help of this thesis.

I would like to thank Tomoko Iwanami, Chikako Ota and Hitomi Wada, the secretaries at iTHEMS,
and Mika Umetani and Satomi Suzuki, the secretaries of particle physics theory group
at Osaka university for arranging a lot of procedures so that I could do my research at RIKEN.
They were always kind and I was helped so many times.
During my Ph.D.~study, I have been supported in part by RIKEN Junior Research Associate program and
by JSPS fellowship for Young Scientists.
Finally, I wish to thank my parents for their understanding, love and constant support.
\end{comment}
\end{abstract}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}



\vfill\eject    % newpage

\tableofcontents



\input{Sections/Sec1}
\input{Sections/Sec2}
\input{Sections/Sec4}
\input{Sections/Sec3}
\input{Sections/Sec5}
\appendix
\input{Sections/SecA}



\clearpage
%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{Sections/Common/endbib}
\bibliographystyle{Sections/Common/JHEP}  %utphys
%\nocite{*}
\bibliography{Sections/Common/toshi}


\end{document}